Final paper detail checks and analyses

### 2021-04-12 Final_analyses_checks_notebook.Rmd
resave

GLAD.prepan.PHQ9 <-  GLAD.prepan %>%
  filter(phq.sum_score_prepan >=9) %>%
  count()

@@

GLAD.base.PHQ9 <-  GLAD.prepan %>%
  filter(phq.sum_score_base >=9) %>%
  count()

>>>>

GLAD.prepan.PHQ9 <-  GLAD.prepan %>%
  filter(phq.sum_score_prepan >=10) %>%
  count()

@@

GLAD.base.PHQ9 <-  GLAD.prepan %>%
  filter(phq.sum_score_base >=10) %>%
  count()
